Evaluating the Effectiveness of Statistical Models in Analyzing Mortality in Canada

### 2024-03-17 outputs/paper.qmd
sort out

## Raw data
First, the original dataset file of "Leading causes of death", named "1310039401-eng", was downloaded from Statistics Canada. Five key variables are included. "Leading cause of death" in the table is defined as an illness or injury that triggers a sequence of events leading directly to death, or an accident or violent situation that results in a fatal injury. The underlying cause is selected from the conditions listed on the medical certificate of cause of death. "Characteristics" contains the "Rank of leading causes of death" which is based on the "Number of deaths". "Age at time of death" is attained at the last birthday preceding death. "Reference period" contains specific numbers, from 2000 to 2022.

@@

### Preview
```{r echo = FALSE}
#| label: tbl-1
#| tbl-cap: "Modeling the most prevalent cause of deaths in Canada, 2000-2022"
cleaned_data <- read.csv("cleaned_data")
cleaned_data <- cleaned_data[, -1]

>>>>

## Raw data
First, the original dataset file of "Leading causes of death", called "1310039401-eng", was downloaded from Statistics Canada and renamed as "raw_data". Five key variables are included. "Leading cause of death" in the table is defined as an illness or injury that triggers a sequence of events leading directly to death, or an accident or violent situation that results in a fatal injury. The underlying cause is selected from the conditions listed on the medical certificate of cause of death. "Characteristics" contains the "Rank of leading causes of death" which is based on the "Number of deaths". "Age at time of death" is attained at the last birthday preceding death. "Reference period" contains specific numbers, from 2000 to 2022.

@@

### Preview
```{r echo = FALSE}
#| label: tbl-1
#| tbl-cap: "Modeling the most prevalent cause of deaths in Canada, 2000-2022"
cleaned_data <- read.csv("inputs/cleaned_data.csv")
cleaned_data <- cleaned_data[, -1]
